---
title: "Total cost and time to treatment initiation for suspected TB patients"
author: "Nathan Green"
date: "07/02/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

## Model

Independent Bayesian linear regressions on cost and time to starting treatment with covariates of sputum smear results ('Not taken', 'Negative', 'Positive') and TB status (missing, 'E;PTB', 'PTB').

## Data

The IDEA dataset for Dosanjh category 1 and 2 patients only.

## Output

Posterior distributions and summary statistics for mean cost and time to starting treatment.

```{r, message=F, warning=F, echo=F}

library(dplyr)
library(tidyr)
library(purrr)
library(knitr)

load(file = "data/out.ls.RData")

nchain <- 1

m.c <- exp(out.ls[[nchain]][, 'mu.c'] + 0.5*out.ls[[nchain]][, 'sigma.c']^2)
m.e <- exp(out.ls[[nchain]][, 'mu.e'] + 0.5*out.ls[[nchain]][, 'sigma.e']^2)


m.c_pred <-
  rep( list(list()), 3) %>%
  setNames(c("", "E;PTB", "PTB"))

m.e_pred <-
  rep( list(list()), 3) %>%
  setNames(c("", "E;PTB", "PTB"))

for (i in 1:3) {
  for (j in 1:3) {
    
    phi.c_pred <- paste0("phi.c_pred[", i, ",", j, "]")
    phi.e_pred <- paste0("phi.e_pred[", i, ",", j, "]")
    
    m.c_pred[[i]][[j]] <- exp(out.ls[[nchain]][, phi.c_pred] + 0.5*out.ls[[nchain]][, 'sigma.c']^2)
    m.e_pred[[i]][[j]] <- exp(out.ls[[nchain]][, phi.e_pred] + 0.5*out.ls[[nchain]][, 'sigma.e']^2)
  }
}
```


```{r, message=F, warning=F, echo=F}
levels_smear <- c("Not taken", "Negative", "Positive")

## for ssm & tbstatus  model
par(mfrow = c(2, 2))

for (i in 1:3) {
  
  hist(as.numeric(m.e_pred$`E;PTB`[[i]]), breaks = 30, xlim = c(0, 130), main = "")
  hist(as.numeric(m.c_pred$`E;PTB`[[i]]), breaks = 40, xlim = c(200, 1400), main = "")
  
  hist(as.numeric(m.e_pred$PTB[[i]]), breaks = 30, xlim = c(0, 150), main = "")
  hist(as.numeric(m.c_pred$PTB[[i]]), breaks = 30, xlim = c(200, 1400), main = "")
  
  mtext(levels_smear[i], side = 3, line = -1, outer = TRUE)
}
```

### All smear results on same plot.

Black - Not taken,
Red - Negative,
Blue - Positive.

```{r, message=F, warning=F, echo=F}
par(mfrow = c(2, 2))

plot(density(as.numeric(m.e_pred$`E;PTB`[[1]])), ylim = c(0,0.12), xlim = c(0,100), main = "Time, E;PTB")
lines(density(as.numeric(m.e_pred$`E;PTB`[[2]])), col = "red")
lines(density(as.numeric(m.e_pred$`E;PTB`[[3]])), col = "blue")

plot(density(as.numeric(m.c_pred$`E;PTB`[[1]])), ylim = c(0,0.005), xlim = c(0, 1800), main = "Cost, E;PTB")
lines(density(as.numeric(m.c_pred$`E;PTB`[[2]])), col = "red")
lines(density(as.numeric(m.c_pred$`E;PTB`[[3]])), col = "blue")

plot(density(as.numeric(m.e_pred$`PTB`[[1]])), ylim = c(0,0.12), xlim = c(0,100), main = "Time, PTB")
lines(density(as.numeric(m.e_pred$`PTB`[[2]])), col = "red")
lines(density(as.numeric(m.e_pred$`PTB`[[3]])), col = "blue")

plot(density(as.numeric(m.c_pred$`PTB`[[1]])), ylim = c(0,0.005), xlim = c(0, 1800), main = "Cost, PTB")
lines(density(as.numeric(m.c_pred$`PTB`[[2]])), col = "red")
lines(density(as.numeric(m.c_pred$`PTB`[[3]])), col = "blue")
```

```{r}
load("data/out.ls_pathprobs.RData")

probs <- out_pathprobs$sims.list$prob
```

```{r, message=F, warning=F, echo=F}
## results tables

library(reshape2)
library(tidyr)

## smm & tbstatus
tribble(~ ssm,       ~'tb status', ~'mean prob',    ~'sd prob',    ~'mean cost',                ~'sd cost',                ~'mean time',                ~'sd time',
        "Not taken", "E;PTB",      mean(probs[,1]), sd(probs[,1]), mean(m.c_pred$`E;PTB`[[1]]), sd(m.c_pred$`E;PTB`[[1]]), mean(m.e_pred$`E;PTB`[[1]]), sd(m.e_pred$`E;PTB`[[1]]),
        "Not taken", "PTB",        mean(probs[,2]), sd(probs[,2]), mean(m.c_pred$`PTB`[[1]]),   sd(m.c_pred$`PTB`[[1]]),   mean(m.e_pred$`PTB`[[1]]),   sd(m.e_pred$`PTB`[[1]]), 
        "Negative",  "E;PTB",      mean(probs[,3]), sd(probs[,3]), mean(m.c_pred$`E;PTB`[[2]]), sd(m.c_pred$`E;PTB`[[2]]), mean(m.e_pred$`E;PTB`[[2]]), sd(m.e_pred$`E;PTB`[[2]]),
        "Negative",  "PTB",        mean(probs[,4]), sd(probs[,4]), mean(m.c_pred$`PTB`[[2]]),   sd(m.c_pred$`PTB`[[2]]),   mean(m.e_pred$`PTB`[[2]]),   sd(m.e_pred$`PTB`[[2]]),
        "Positive",  "E;PTB",      mean(probs[,5]), sd(probs[,5]), mean(m.c_pred$`E;PTB`[[3]]), sd(m.c_pred$`E;PTB`[[3]]), mean(m.e_pred$`E;PTB`[[3]]), sd(m.e_pred$`E;PTB`[[3]]),
        "Positive",  "PTB",        mean(probs[,6]), sd(probs[,6]), mean(m.c_pred$`PTB`[[3]]),   sd(m.c_pred$`PTB`[[3]]),   mean(m.e_pred$`PTB`[[3]]),   sd(m.e_pred$`PTB`[[3]])) %>%
  mutate_if(is.numeric, round, 2) %>% 
  kable()
```

# References
